Refinements for open automata

### 2022-06-17 2021-Refinement/paper/refinementarticle.tex
Thm2 suite

Because of the domain of the substitutions of the relations, the formula can be re-written:
\begin{multline*}
V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\mpar{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}
The formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$. To build $R_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to\\ ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
\begin{multline*}
V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \uplus  \biguplus_\subbox{p \in P} \fvars{t_{2px}} \vdash\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1} \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P}
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}
Indeed, since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$ we have:
\begin{align*}
R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}  \\  
\implies R_{13}\mpar{s'_1,s'_{3pxy}}
\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}  \\ 
\implies R_{13}\mpar{s'_1,s'_{3pxy}}\psubst{\psi_1  \uplus \psi_{3pxy}}
\end{align*}
This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition  with note that $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$:
\begin{multline*}
V_1  \uplus V_3  \uplus \fvars{t_1} \vdash\\
R_{13}(s_1,s_3)  \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P}
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \\ \wedge g_{3pxy} 
{\wedge R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}
Overall, we have a family of open transitions $t^{p\in P,x\in X,y\in Y}_{pxy} \subseteq T_3$ that should simulate $t_1$. All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of  open transitions.  This allows us to get the desired conclusion, that there is a set of  open transitions indexed over $Z$:
%This provides the desired conclusion:\\
\begin{multline*}
V_1 \uplus  V_3 \uplus \fvars{t_1}
\vdash\\\hspace{2em}
\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
{R_{13}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
\end{array}}}
\end{multline*}	
\item  Finally, we have to prove the following holds:
\begin{multline*}
\forall \mpar{s_1, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_1, t_3} = \mpar{\OTx{1}{}{1}{1}, \OTx{3}{}{3}{3}} \in \fOT{s_1} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R\mpar{s_1, s_3} \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_3} \beta_{1j} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
 R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}
\end{multline*}
According to the refinement relation between  $A_1$ and $A_2$ we have:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
 R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
\end{multline*}
Yet according to the relation between   $A_2$ and $A_3$ we have:

\begin{multline*}
\forall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
\implies \\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
 R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}\\
\end{multline*}

------------------------------

$\forall \mpar{s_1,s_3} \in S_1 \times S_3$, $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$
\begin{multline*}
V_1 \uplus V_3 \uplus \fvars{t_1}  \uplus \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \\ g_1 \wedge g_{2} \wedge g_{3}
\wedge \alpha_1 = \alpha_{3}  \wedge \bigwedge_\subbox{j \in J'_1\cap  J'_{3}} \beta_{1j} = \beta_{3j}
 \implies R_{13}\mpar{s'_1, s'_3} \psubst{\psi_1 \uplus \psi_3 } 
\end{multline*}

According to the refinement relation between  $A_1$ and $A_2$ we have, for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$:
\begin{multline*}
\bigsymb{\forall} \mpar{t_1, t_{2}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j} \implies  R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2}
\end{multline*}

Yet according to the relation between   $A_2$ and $A_3$ we have  $\forall \mpar{s_2,s_3} \in S_2 \times S_3$ and
\begin{multline*}
\bigsymb{\forall} \mpar{t_2, t_{3}} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\  V_2 \uplus V_3 \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j} \implies  R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
\end{multline*}

We can make the conjunction of these two formulas.  For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $. Thus, we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$  
\begin{multline*}
V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash\\ \left(R_{12}\mpar{s_1, s_2} \wedge   g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j}\right) \wedge \hspace{2.5cm}\\ \mpar{R_{23}\mpar{s_2, s_3} 
\wedge  g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j}} \implies\\ R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2} \wedge R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
\end{multline*}
Note that if  $R_{12}\mpar{s_1, s_2}$ or $ \mpar{R_{23}\mpar{s_2, s_3}}$ is false the statement trivially holds.

By rearranging and simplifying we get:$\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$, $ \bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \\\mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$\\
\begin{multline*}
V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \underbrace{R_{12}\mpar{s_1, s_2} \wedge  R_{23}\mpar{s_2, s_3}}_{R_{13}\mpar{s_1, s_3}} \wedge \\ g_1  \wedge g_{3}
\wedge \alpha_1 = \alpha_{3}  \wedge \bigwedge_\subbox{j \in J'_1\cap J'_2 \cap J'_{3}} \beta_{1j} = \beta_{3j}
 \implies \underbrace{R_{12}\mpar{s'_1, s'_{2}}\wedge R_{23}\mpar{s'_2, s'_{3}}}_{R_{13}\mpar{s'_1, s'_3}} \psubst{\psi_1 \uplus \psi_2\uplus \psi_3 } 
\end{multline*}
By removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.

@@

Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$.
We obtain 
\[
t_{13x}' = \OT{\mpar{s_1, s_3}}{\mpar{s_{1x}, {s_3}}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x} \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{1x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{1xk}}{\psi_{1x} \uplus \psi^2_3} \qquad \text{ where } k \in J'_{1x} 
\]

This specifies the family $\mpar{t_{13x}'}^{x\in X}$
that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive from the property ($\star$) and from the definition of $t_{13x}'$ and $t_{23}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
 R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
\end{multline*}

>>>>

Because of the domain of the substitutions of the relations, the formula can be re-written:
\begin{multline*}
V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\mpar{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}
The formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$. To build $R_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to\\ ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
\begin{multline*}
V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \uplus  \biguplus_\subbox{p \in P} \fvars{t_{2px}} \vdash\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1} \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P}
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}
Indeed, since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$ we have:
\begin{align*}
R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}  \\  
\implies R_{13}\mpar{s'_1,s'_{3pxy}}
\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}  \\ 
\implies R_{13}\mpar{s'_1,s'_{3pxy}}\psubst{\psi_1  \uplus \psi_{3pxy}}
\end{align*}
This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition  with note that $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$:
\begin{multline*}
V_1  \uplus V_3  \uplus \fvars{t_1} \vdash\\
R_{13}(s_1,s_3)  \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P}
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \\ \wedge g_{3pxy} 
{\wedge R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}
Overall, we have a family of open transitions $t^{p\in P,x\in X,y\in Y}_{pxy} \subseteq T_3$ that should simulate $t_1$. All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of  open transitions.  This allows us to get the desired conclusion, that there is a set of  open transitions indexed over $Z$:
%This provides the desired conclusion:\\
\begin{multline*}
V_1 \uplus  V_3 \uplus \fvars{t_1}
\vdash\\\hspace{2em}
\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
{R_{13}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
\end{array}}}
\end{multline*}

\item  Finally, we have to prove the following holds:
\begin{multline*}
\forall \mpar{s_1, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_1, t_3} = \mpar{\OTx{1}{}{1}{1}, \OTx{3}{}{3}{3}} \in \fOT{s_1} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{13}\mpar{s_1, s_3} \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_3} \beta_{1j} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
 R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}
\end{multline*}
According to the refinement relation between  $A_1$ and $A_2$ we have:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
 R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
\end{multline*}
Yet according to the relation between   $A_2$ and $A_3$ we have:

\begin{multline*}
\forall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{1 x}\land
 R_{23}\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
\end{multline*}

For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $. 
We can make the conjunction of these two formulas,
we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and\\ $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$  
\begin{multline*}
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \bigsymb{\bigexists} 
\mpar{t_{2x} = \OTx{2}{y}{2y}{2y} \in \fOT{s_2}}^{y \in Y},\\
 V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \uplus \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \biguplus_{y\in Y}\fvars{t_{2y}}   \vdash \hspace{6cm}\\  \mpar{R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2} \wedge \mpar{ R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 }
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j}} 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
 R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}} \wedge\\
\bigsymb{\bigwedge_{y\in Y}}
\mpar{
\alpha_2=\alpha_{2 y}  \land J'_{2y}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2yj}\land g_{1 y}\land
 R_{23}\mpar{s'_{2 y}, s'_3}\psubst{\psi_{2 y} \uplus \psi_3}}\\
\end{multline*}

Note that if  either $R_{12}\mpar{s_1, s_2}$ or $R_{23}\mpar{s_2, s_3}$ is false the statement trivially holds.

By rearranging and simplifying we get:$\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$, $ \bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \\\mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$\\

\TODO{Manque Argument de simplification mecanique a trouver}
By removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.

@@

Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_1$ and compose it with $t_3^2$.
We obtain 
\[
t_{13x}' = \OT{\mpar{s_1, s_3}}{\mpar{s_{1x}, {s_3}}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x} \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{1x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{1xk}}{\psi_{1x} \uplus \psi^2_3} \qquad \text{ where } k \in J'_{1x} 
\]

This specifies the family $\mpar{t_{13x}'}^{x\in X}$
that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
 R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
\end{multline*}
Furthermore, from the property ($\star$) and from the definition of $t_{13x}'$:
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\Big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
  \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\Big) \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\\
 \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
 \end{multline*}
 \TODO{to check $j \in J'_2 \setminus\{k\}$}
